### 2019-07-02 manuscript.tex
Update manuscript.tex

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{AdnrLesc16, UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01} and Tostan (https://www.tostan.org/programs/community-empowerment-program/).

>>>>

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15, with another 15 millions girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade if the trends continue \cite{KhosBane17, UNIC16}.  FGC is also known as female genital mutilation and female circumcision.  As adapted by Tostan \cite{Tost15}, cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}
